### 2016-07-11 forgerard.tex
remove third model for now

The next level of complexity to add is intrinsic dispersion through stochastic parameters that describe the global  covariance matrices
$C_{c}$ and a grey dust $\Delta$.  The model would then look like
\begin{equation*}
\left(
\begin{matrix}
U\\B\\V\\R\\I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\Delta +
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
\end{matrix}
\right)
,C_{c}
\right),
\end{equation*}
\begin{equation*}
\Delta \sim \mathcal{N}(0,\sigma^2_\Delta),
\end{equation*}
\begin{equation*}
\left(
\begin{matrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right).
\end{equation*}
For boundary conditions we set  $\langle k \rangle=0$ and we set $\gamma_2=1$.

The next level of complexity to add an intrinsic color variation modeled with a single parameter $d$.  The model would then look like
\begin{equation*}
\left(
\begin{matrix}
U\\B\\V\\R\\I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\Delta +
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \delta_0 d \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \delta_1 d\\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \delta_2 d\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \delta_3 d\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} + \delta_4 d
\end{matrix}
\right)
,C_{c}
\right),
\end{equation*}

>>>>

The next level of complexity to add is intrinsic dispersion through stochastic parameters that describe the global  covariance matrices
$C_{c}$ and a grey dust $\Delta$.  The model would then look like
\begin{equation*}
\left(
\begin{matrix}
U\\B\\V\\R\\I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\Delta +
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
\end{matrix}
\right)
,C_{c}
\right),
\end{equation*}
